OptiFit: a new method for fitting amplicon sequences to existing OTUs

### 2021-09-01 paper/paper.Rmd
Can we just not with 'robust'? ISO a better word.

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

@@

<!-- TODO
- "require" and "enforce" for opti -- wrong word choice.
- be consistent with cluster, assign, fit, and map.
-->

>>>>

---
title: "OptiFit: a new method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

@@

<!-- TODO
- "require" and "enforce" for opti -- wrong word choice.
- be consistent with cluster, assign, fit, and map.
- can we replace "robust" with something better / more specific?
-->
